---
title: "Fog Detection"
author: "Martin Roth and Andrea Pagani"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fog Detection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width  = 7,
  fig.height = 4
)
```

## Example how to use visDec
### Load required libaries
```{r, include=FALSE, message=FALSE}
library(imager)
library(data.table)
library(ggplot2)
library(visDec)
library(foreach)
library(iterators)
library(doParallel)
registerDoParallel(cores=2)
```

#### Read example pictures
```{r, ExamplePictures}
path <- system.file("extdata/Meetterrein", package="visDec")
filenames <- list.files(path,
                        pattern=glob2rx("Meetterrein_201510*.jpg"),
                        full.names=TRUE)
#```{r, BaseInformationAndFiltering}
imageSummary <- foreach(file = iter(filenames), .combine = rbind) %dopar% {
  FileNameParser(file, "na*me_yyyymmdd_hhmm.jpg")
}
```

```{r, FilterImages}
#daylightImages <- FilterDayLightHours(imageSummary, properties, 0, 0)
daylightImages <- imageSummary 
```

```{r, FeatureCalculation}
invisible(daylightImages[, id := 1:.N])
setkey(daylightImages, id)

imageFeatures <- foreach(id = iter(daylightImages[, id]), .combine = rbind) %dopar% {
  daylightImages[id, ImageFeatures(filePath, y > 16)]
}
```

```{r, JoinFeatures}
setkey(daylightImages, filePath)
setkey(imageFeatures, filePath)

imageSummary <- merge(daylightImages, imageFeatures)
```

### Edges in a clear situation
```{r, EdgesPlotFoggy, echo=FALSE}
im <- subim(load.image(filenames[75]), y > 16)
old_par <- par(mfrow=c(1,2))
plot(im)
DetectEdges(im) %>% plot
par(old_par)
```

### Edges in a foggy situation
```{r, EdgesPlotClear, echo=FALSE}
im <- subim(load.image(filenames[49]), y > 16)
old_par <- par(mfrow=c(1,2))
plot(im)
DetectEdges(im) %>% plot
par(old_par)
```

### Load sensor values
```{r, SensorFiles, fig.show='hold'}
path <- system.file("extdata/Sensor", package="visDec")
sensorFiles <- list.files(path,
                          pattern=glob2rx("DeBilt*.csv"),
                          full.names=TRUE)
sensorData <- ReadMORSensorData(sensorFiles)
setkey(sensorData, dateTime)
setkey(imageSummary, dateTime)
imageSummary <- merge(imageSummary, sensorData)
invisible(imageSummary[, MOR := TOA.MOR_10]) # see .e.g https://github.com/rstudio/rmarkdown/issues/829
```

### Time series
```{r, TimeSeries, fig.show='hold'}
ggplot(imageSummary, aes(x = dateTime, y = meanEdge)) + geom_line() + xlab("")
ggplot(imageSummary, aes(x = dateTime, y= MOR)) + geom_line() +
  xlab("") 
ggplot(imageSummary,
       aes(x = dateTime, y = fractalDim)) + geom_line() + xlab("")
```

```{r, DayOnly, fig.show='hold'}
ggplot(imageSummary[hour(dateTime) %in% seq(5, 10, by=1), ],
       aes(x = dateTime, y = meanEdge)) + geom_line() + xlab("")
ggplot(imageSummary[hour(dateTime) %in% seq(5, 10, by=1), ],
       aes(x = dateTime, y = fractalDim)) + geom_line() + xlab("")
```

### Scatter plots
```{r, ScatterPlots, fig.show='hold'}
invisible(imageSummary[, visibility := factor(2000)])
invisible(imageSummary[MOR < 1000, visibility := factor(1000)])
invisible(imageSummary[MOR < 500, visibility := factor(500)])
invisible(imageSummary[MOR < 200, visibility := factor(200)])
#ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(FS261), y = meanEdge, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(MOR), y = meanEdge, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(MOR), y = changePoint, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(MOR), y = smoothness, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(MOR), y = fractalDim, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(MOR), y = meanHue, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(MOR), y = meanSaturation, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
ggplot(imageSummary[hour %in% seq(7, 16, by = 1), ], aes(x = log(MOR), y = meanBrightness, col = visibility)) + geom_point() + geom_quantile(aes(col=NULL), quantiles=0.5)
```

```{r, echo=FALSE}
stopImplicitCluster()
```
